---
title: "IST 707 Final Code"
output:
  pdf_document: default
  html_notebook: default
---

 
```{r}
library(readr)
library(tidyverse)
library(caret)
library(stringr)
```

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
salaries <- read_csv("salaries.txt")
general <- read_csv("general_stats.txt")
advanced <- read_csv("advanced_stats.txt")
```
 
#cleanup
```{r}
#cleaning up salary table

names(salaries) <- salaries[1,]

salaries <- salaries %>% select("Player", "2021-22", "2022-23")

salaries <- salaries[-1,]

salaries
```

```{r}
#joining the tables

data <- inner_join(x = salaries, y = general, by = "Player")

data <- inner_join(x = data, y = advanced, by = "Player")
```

```{r}
#creating data table that still has name

name_data <- data %>% select(-c(Rk.x, Tm.x, G.x, GS, Rk.y, Tm.y, Pos.y, Pos.x, Age.y, G.y, MP.y,
                           "ORB%", "DRB%", "TRB%", "AST%", "STL%", "BLK%", "TOV%", "...20", "OWS", "DWS", "WS",
                           "...25","OBPM","DBPM","BPM"))
```


```{r}
#removing unwanted columns

data <- data %>% select(-c(Rk.x, Tm.x, G.x, GS, Rk.y, Tm.y, Pos.y, Pos.x, Age.y, G.y, MP.y,
                           "ORB%", "DRB%", "TRB%", "AST%", "STL%", "BLK%", "TOV%", "...20", "OWS", "DWS", "WS",
                           "...25","OBPM","DBPM","BPM", "Player"))
```


```{r}
#making free agent table
free_agents <- salaries
free_agents <- free_agents %>% filter(is.na(`2022-23`)) %>% 
  select(Player) %>% unique() %>% na.omit()

free_agents <- left_join(x = free_agents, y = name_data, by = "Player") %>% 
  select(-`2022-23`) %>% unique() %>% na.omit(FG)
```

```{r}
#removong dollar sign from free agent table and making numeric

names(free_agents)[2] <- "salary"

free_agents <- free_agents %>% mutate(salary = str_sub(string = salary, start = 2, end = str_length(salary)))

free_agents$salary <- as.numeric(free_agents$salary)

str(free_agents)
```


```{r}
#pre processing 
names(data)[1] <- "salary"

data <- data %>% mutate(salary = str_sub(string = salary, start = 2, end = str_length(salary)))

data$salary <- as.numeric(data$salary)

str(data)
```

```{r}
data <- data %>% drop_na(salary) %>% select(-`2022-23`)

#make the rest na into 0

data[is.na(data)] <- 0
```

##Making buckets
```{r}
# dataBuckets <- data$salary %>% cut(breaks = seq(from = 0, to = 48000000, by = 4000000))
# 
# data2 <- data
# 
# data2$salary <- dataBuckets
# 
# levels(data2$salary) <- c('0-4mil', '4mil-8mil', '8mil-12mil', 
#                           '12mil-16mil', '16mil-20mil' , '20mil-24mil', '24mil-28mil', 
#                           '28mil-32mil', '32mil-36mil' , '36mil-40mil' , '40mil-44mil' , 
#                           '44mil-48mil' )
```

##BUILDING MODEL

```{r}
set.seed(40)
# 
# index <- sample(x = nrow(data), size = floor(0.75*nrow(data)))
# 
# train <- data[index,]
# 
# test <- data[-index,]
```


```{r}
#using non free agents as train, and making buckets

data3 <- name_data %>% subset(Player %in% free_agents$Player == FALSE) %>% unique() %>% 
  select(-c(Player, `2022-23`))

names(data3)[1] <- "salary"

data3 <- data3 %>% mutate(salary = str_sub(string = salary, start = 2, end = str_length(salary)))

data3$salary <- as.numeric(data3$salary)

dataBuckets3 <- data3$salary %>% cut(breaks = seq(from = 0, to = 48000000, by = 4000000))

data3$salary <- dataBuckets3

levels(data3$salary) <- c('0-4mil', '4mil-8mil', '8mil-12mil', 
                          '12mil-16mil', '16mil-20mil' , '20mil-24mil', '24mil-28mil', 
                          '28mil-32mil', '32mil-36mil' , '36mil-40mil' , '40mil-44mil' , 
                          '44mil-48mil' )

data3 <- data3 %>% na.omit(salary)
```

```{r}
#making free agents train data

# free_agent_names <- free_agents$Player
# 
# free_agents <- free_agents %>% select(-Player)

freeBuckets3 <- free_agents$salary %>% cut(breaks = seq(from = 0, to = 48000000, by = 4000000))

free_agents$salary <- freeBuckets3

levels(free_agents$salary) <- c('0-4mil', '4mil-8mil', '8mil-12mil', 
                          '12mil-16mil', '16mil-20mil' , '20mil-24mil', '24mil-28mil', 
                          '28mil-32mil', '32mil-36mil' , '36mil-40mil' , '40mil-44mil' , 
                          '44mil-48mil' )

```



##RF Model with integers as opposed to classification
# ```{r}
# control <- trainControl(method='repeatedcv', 
#                         number=10, 
#                         repeats=3)
# ```
# 
# ```{r}
# rf_model <- train(salary~.,
#                       data=train,
#                       method='rf',
#                       metric='RMSE',
#                       trControl=control)
# 
# write_rds(rf_model, "rf_model.rds")
# ```
# 
# ```{r}
# #prediction
# preds <- predict(rf_model, test)
# ```
# 
# ```{r}
# new <- data.frame(preds, test$salary)
# new
# ```
# 
# ```{r}
# rf_model
# ```
This code did not end up telling me much, so I will not include it in my writeup. It is also using random train and test data in a 75% splits, as opposed to using the free agents as the test data.


## Building main model with buckets

```{r}
set.seed(50)

# index <- sample(x = nrow(data2), size = floor(0.75*nrow(data2)))
# 
# train2 <- data2[index,]
# 
# test2 <- data2[-index,]
```

```{r}
#went up from 51 to 61 with tuning
tuneGrid <- expand.grid(.mtry = (1:5))
```


```{r}
rf_model2 <- train(salary~.,
                      data=data3,
                      method='rf',
                      metric='Accuracy',
                      trControl=control,
                      tuneGrid = tuneGrid)

write_rds(rf_model2, "rf_model2.rds")
```


##Prediction
```{r}
#prediction

preds2 <- predict(rf_model2, free_agents)
```

```{r}
confusionMatrix(preds2, free_agents$salary)
```

```{r}
free_agent_names <- data.frame(free_agent_names)
free_agent_predictions <- cbind(preds2, free_agents$salary, free_agent_names)
```


### RUNNING SVM MODEL

```{r}
svm_model <- train(salary~.,
                      data=data3,
                      method='svmLinear',
                      metric='Accuracy',
                      trControl=control,
                      preProcess = c("center","scale"))
```

#SVM predictions


```{r}
#prediction

svm_preds <- predict(svm_model, free_agents)
```

```{r}
confusionMatrix(svm_preds, free_agents$salary)
```


